---
title: "`dplyr` Weekend Homework"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```
<br>



As this is your first weekend homework, here are some tips: 

* Try to schedule some time in your weekend to work on the homework so it's not suddenly Monday morning and you haven't gotten started yet (it happens).
* Remember that the weekend homework is for your learning, so try to use it as an opportunity to apply and consolidate everything you've learned in the week.
* Also use it as an opportunity to spend a bit more time making your code readable and reproducible, by practising commenting and writing some text around your steps and findings. You will thank yourself later! 
  * This will be especially useful for this specific weekend homework as it's very open-ended and you will eventually forget your own thought process
* A bit obvious, but don't spend your entire weekend working on the homework! Remember to spend time doing things you enjoy and rest up ahead of the following week.

The data for this weekend homework is scraped from Goodreads (a website all about books) and made publicly available on Kaggle. You can read more about the data [here](https://www.kaggle.com/jealousleopard/goodreadsbooks).

# MVP

### First steps

Load necessary packages and read in `books.csv`. Investigate dimensions, variables, missing values - you know the drill!

```{r}
library(tidyverse)
books <- read_csv("data/books.csv")
```

```{r}
nrow(books)
ncol(books)
dim(books)
names(books)
head(books, 10)
tail(books, 10)
glimpse(books)
view(books)
str(books)
```

```{r}
books %>% 
  summarise(na_count = sum(is.na(books)))
```


### Up to you

Now it's up to you... For this weekend homework there will be no specific tasks, just you and this dataset! Using everything you've learned this week, try to describe/summarise at least 5 things about this dataset - using R and the tidyverse of course! Feel free to find and use new functions if there is something that the tidyverse doesn't offer, but do try to use this homework to apply what you have learned this week. Be prepared to share one of your findings on Monday!

### Remember

Before you submit, go through your weekend homework and make sure your code is following best practices as laid out in the `coding_best_practice` lesson.



1. First off I would like to find out what the 10 highest rated books are. There are a few books that have perfect ratings and not many total ratings, so I'll filter these out. Will only include books that have at least 1000 total ratings.

```{r}
books %>% 
  select(title, authors, average_rating, ratings_count) %>%
  filter(ratings_count > 1000) %>% 
  arrange(desc(average_rating)) %>% 
  head(10)
```


2. Checking how many books published per language and ranking the languages per number of books.

```{r}
books %>% 
  group_by(language_code) %>% 
  summarise(language_count = n()) %>% 
  arrange(desc(language_count))
```


3. Checking which authors have the highest rated books overall. Filtering out books that have less than 1000 ratings.

```{r}
books %>% 
  select(authors, average_rating, ratings_count) %>%
  filter(ratings_count > 1000) %>%
  # tried to filter out any authors who had collaborated with someone else by removing any rows that contained "/" but could not get it to work
  group_by(authors) %>% 
  summarise(mean(average_rating)) %>%
  arrange(desc(`mean(average_rating)`))
```


4. Ranking the publishers by number of books published.

```{r}
books %>% 
  select(publisher) %>% 
  group_by(publisher) %>% 
  summarise(books_published = n()) %>% 
  arrange(desc(books_published))
```

John's example:

```{r}
books %>% 
  count(publisher, sort = TRUE)
```



5. Ranking all books by rate of text reviews to numeric ratings.

```{r}
books %>% 
  select(title, ratings_count, text_reviews_count) %>% 
  filter(ratings_count > 10) %>% 
  mutate(text_rate = text_reviews_count / ratings_count) %>% 
  arrange(desc(text_rate))
```


6. Ranking authors by total number of pages written.

```{r}
books %>% 
  select(authors, num_pages) %>% 
  # again would've liked to implement a way of filtering out collaborative efforts but couldn't quite figure it out
  group_by(authors) %>% 
  summarise(sum(num_pages)) %>% 
  arrange(desc(`sum(num_pages)`))
```



These are equivalent:

```{r}
books %>% 
  count(language_code)
```

```{r}
books %>%
  group_by(language_code) %>% 
  summarise(n = n())
```

