---
title: "Distributions homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

You are given a cut of a database containing details of mobile phones and their customer reviews on an online shopping site in file `20190928-items.csv`. Each row in the data corresponds to one model of mobile phone. Use the data to answer the following questions.  

As part of the MVP we want you not to just run the code but also have a go at **intepreting the results** - this is the **main learning objective** from this homework. Don't worry if you aren't sure, it's ok to get it wrong, but give it a go, through trying we will learn. 

# MVP


**Question 1.**  
Load the data, `clean_names()` and explore it.

<br>

```{r}
library(janitor)
library(tidyverse)
```

```{r}
phones <- read_csv("data/20190928-items.csv") %>% 
  clean_names()
```


**Question 2.**  
Find the brand with the highest numbers of phones in the dataset.

<br>

```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(n())
```

Samsung has the highest number of phones in the dataset (397).


**Question 3.**  
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?<br>
<details>
<summary>**Hint**</summary>
You will need to calculate the `mean()` and `sd()` of the ratings to plot the appropriate normal distribution. Alternatively, investigate using the `fitdistr()` function in the `MASS` package]
</details>
<br>

```{r}
samsung <- phones %>% 
  filter(brand == "Samsung") %>% 
    summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )

samsung
```

```{r}
phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung$mean,
      sd = samsung$sd
    ),
    col = "green"
  )
```

Looking at the plot, it seems that the data has normal distribution. There do appear to be some outliers, we can check this with the following code.

```{r}
phones_scaled <- phones %>% 
  filter(brand == "Samsung") %>% 
  mutate(z_rating = scale(rating))

phones_scaled
```

Checking for outliers:
```{r}
phones_scaled %>% 
  filter(!between(z_rating, left = -3, right = 3))
```
There are eight outliers (one star ratings).


**Question 4.**  
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the `mean()` and `sd()` of your distribution in an earlier question. Use these values to calculate the *proportions* of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.  


```{r}
count <- phones_scaled %>% 
  filter(between(z_rating, left = -1, right = 1)) %>% 
  nrow()

pnorm(q = 1) - pnorm(q = -1)

count / nrow(phones_scaled)
```
79% of ratings fall within one standard deviation of the mean, which is more than the 68% we would expect from a normal distribution.

```{r}
count <- phones_scaled %>% 
  filter(between(z_rating, left = -2, right = 2)) %>% 
  nrow()

pnorm(q = 2) - pnorm(q = -2)

count / nrow(phones_scaled)
```
92% of ratings fall within two standard deviations of the mean, very close to the 95.4% we would expect from a normal distribution.

```{r}
count <- phones_scaled %>% 
  filter(between(z_rating, left = -3, right = 3)) %>% 
  nrow()

pnorm(q = 3) - pnorm(q = -3)

count / nrow(phones_scaled)
```
98% of ratings fall within three standard deviations of the mean, very close to the 99.7% we would expect from a normal distribution.

We can conclude that the Samsung ratings data follows a normal distribution.


<details>
<summary>**Hint**</summary>
You can use a `filter()` to get only the ratings within one-, two- and three standard deviations of the mean, and then think about how to calculate what proportion each of these filtered sets make of the total number of ratings. You'll need to use three separate `filter()` and `summarise()` pipes to do this.
</details>

<details>
<summary>**Further hint - code to filter within one SD**</summary>
Here's the code to filter and summarise the proportion of ratings within one standard deviation of the mean.
```{r, eval=FALSE}
samsung_ratings %>%
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
</details>

# Extension

Investigate the use of the `qqnorm()` plot in R to determine whether data is normally distributed. What is a 'quantile-quantile plot'? What do we expect to see in a `qqnorm()` plot if data is nearly normally distributed?

Here are a few resources:

* [Understanding QQ plots](https://data.library.virginia.edu/understanding-q-q-plots/)
* [Short video tutorial](https://www.youtube.com/watch?v=Erze9pNIX8A) (the presenter doesn't use RStudio, but the commands are the same. Just ignore the final comments on hypothesis tests for now.)
* [Longer video tutorial](https://www.youtube.com/watch?v=smJBsZ4YQZw)
* [Quantile-Quantile plots - R Base Graphs](http://www.sthda.com/english/wiki/qq-plots-quantile-quantile-plots-r-base-graphs)

