---
title: "Text Mining Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, fig.align = "center", message = FALSE, warning = FALSE)
```

```{r}
library(tidytext)
library(tidyverse)
library(janeaustenr)
```

# MVP

Using the dataset `austen_books()` from the package `janeaustenr`:

1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

```{r}
austen_books <- austen_books()
```

```{r}
pride <- austen_books %>% 
  filter(book == "Pride & Prejudice") %>% 
  select(text) %>% 
  unnest_tokens(word, text)

sense <- austen_books %>% 
  filter(book == "Sense & Sensibility") %>% 
  select(text) %>% 
  unnest_tokens(word, text)
```

```{r}
pride %>% 
  count(word, sort = TRUE)

sense %>% 
  count(word, sort = TRUE)
```

2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

```{r}
pride %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)

sense %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
pride %>%
  inner_join(get_sentiments("bing")) %>% 
  count(word, sort = TRUE)

sense %>%
  inner_join(get_sentiments("bing")) %>% 
  count(word, sort = TRUE)
```

# Extension

Taking your results above. Can you create a plot which visualises the differences between the books?  

```{r}
pride %>%
  inner_join(get_sentiments("afinn")) %>% 
  summarise(mean(value))

sense %>%
  inner_join(get_sentiments("afinn")) %>% 
  summarise(mean(value))
```

